UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-15 files/paper/paper.tex
JUNAED: Edited and left comments as 'starnotes' in the file. Please ensure you address those, and fix all the references to images. Do not hardcode image numbers, but use \ref and \labels. I have fixed figure 1, so use that as a reference.

\documentclass[conference,reqno]{IEEEtran}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

@@

@@

\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}

\author{\IEEEauthorblockN{Cameron Fabbri}
\IEEEauthorblockA{Information Directorate\\
Air Force Research Laboratory \\
Rome, NY, USA.\\
cameron.fabbri@us.af.mil}
\and
\IEEEauthorblockN{Md Jahidul Islam}
\IEEEauthorblockA{University of Minnesota- Twin Cities\\
MN, USA.\\
islam034@umn.edu }
\and
\IEEEauthorblockN{Junaed Sattar}
\IEEEauthorblockA{University of Minnesota- Twin Cities\\
MN, USA.\\
junaed@umn.edu
}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Autonomous underwater robots often rely on visual input for decision making due to its non-intrusive and passive nature.
However, due to many factors such as light refraction, particles in the water, and color distortion, images are often times very noisy.
This paper propose a method using Generative Adversarial Networks (GANs) to denoise underwater images, and show that these 
images provide both increased accuracy for an underwater tracking algorithm, as well as a more visually appealing image.
Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of underwater image reconstruction.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}
TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.
Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
color.

As color and illumination begin to change with the depth, vision based algorithms must be very generalizable in order
to work within the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a
variety of underwater data, as well as the high amount of noise introduced, many algorithms may perform poorly in
these different domains. Figure 1 shows the high variability that may occur in underwater environments. A step towards a
solution to this
issue is to be able to restore the images such that they appear to be above water, i.e., with colors corrected and
particles removed. By performing a many to one mapping of these domains from underwater to not underwater (what the
image would look like in the air), algorithms that have

@@

\end{tabular}
\caption{Sample underwater images displaying the diversity of distortion that can occur. \textbf{Maybe say something about how
some images lost all color, but some kept some color for close objects.}}
\end{figure}

\noindent difficulty performing across multiple forms of noise may be able to focus only one clean domain.

Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of
vision. Often times, these networks recquire large amounts of data, either labeled or paired with ground truth.
For the problem of automatically colorizing grayscale images, paired training data is essentially free due to the
fact that any color image can be converted to black and white. However, underwater images distorted by either color
or some other visual effect lack ground truth. We use the recently proposed CycleGAN \cite{zhu2017unpaired}, which
learns to translate an image from domain $X$ to domain $Y$, as a way to generate a paired dataset. By letting $X$ be
a set of undistorted underwater images, and $Y$ be a set of distorted underwater images, we can generate an image
that appears to be underwater while retaining ground truth.

@@

>>>>

\documentclass[letterpaper, 10pt, conference]{ieeeconf}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{url}
\usepackage{hyperref} % JS: Remove this if you cannot compile.

\pdfminorversion=4
% Junaed's definition of a sidenote to look into
\newcommand{\marginlabel}[1]{\mbox{}\marginpar[\raggedleft\hspace{0pt}{#1}]{
\raggedright\hspace{0pt}{#1}}}
\newcommand{\starnote}[1]{\marginlabel{$\bigstar$}\textbf{[#1]}}
\newcommand{\nostarnote}[1]{}
\newcommand{\baad}[1]{} 
% End Junaed's definition

\IEEEoverridecommandlockouts
\overrideIEEEmargins

% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

@@

\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA. \newline
 {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu} 
}
}

% \author{\IEEEauthorblockN{Cameron Fabbri$^{1}$}
% \IEEEauthorblockA{Information Directorate\\
% Air Force Research Laboratory \\
% Rome, NY, USA.\\
% cameron.fabbri@us.af.mil}
% \and
% \IEEEauthorblockN{Md Jahidul Islam \& Junaed Sattar}
% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities, MN, USA.\\
% \{islam034, junaed\}@umn.edu }
% \and
% \IEEEauthorblockN{Junaed Sattar}
% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities,MN, USA.\\
% junaed@umn.edu
%}

@@

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Autonomous underwater vehicles (AUVs) rely on a variety of sensors -- acoustic, inertial and visual -- for intelligent decision making. Due
to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, particularly at shallower
depths. However, factors such as light refraction and absorption, suspended particles in the water, and color distortion affect the quality
of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus face difficult challenges, and consequently
exhibit poor performance on vision-driven tasks. This paper proposes a method to improve the quality of visual underwater scenes using
Generative Adversarial Networks (GANs), with the goal of improving input to vision-driven behaviors further down the autonomy
pipeline. Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of such underwater image
reconstruction\starnote{Reconstruction meaning what we are doing here, right? So this is a contribution too, to show how CycleGAN is used to
generate the dataset, correct?}. For any visually-guided underwater robots, this improvement can result in increased safety and reliability
through robust visual perception. To that effect, we present quantitative and qualitative data which demonstrates that images corrected
through the proposed approach generate more visually appealing images, and also provide increased accuracy for an underwater diver tracking
algorithm.
\end{abstract}

%\IEEEpeerreviewmaketitle

\section{Introduction}
TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
do this?}  Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual sensing is an
attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs \cite{shkurti2012multi},
deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed\starnote{Citation?} are a number of tasks where
visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not exposed to
the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out in the
past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such as light
refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect worsens, as more
and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, such as the
amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera being
used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of color.

As color and illumination begin to change with the depth, vision-based algorithms must need to be very generalizable in order to work within
the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater data to train a visual
system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these different
domains. Figure~\ref{fig:samples}\starnote{DO NOT USE HARDCODED FIGURE NUMBERS!!! Use a label\{\} right before the caption, and then refer
to it using the ref\{\} command as I have done here -- see the \LaTeX source.} shows the high variability in visual scenes that may occur in
underwater environments. A step towards a solution to this issue is to be able to restore the images such that they appear to be above
water, \emph{i.e.}, with colors corrected and suspended particles removed from the scene. By performing a many-to-one mapping of these
domains from underwater to not underwater (what the image would look like above water), algorithms that have difficulty performing across
multiple forms of noise may be able to focus only one clean domain.

@@

\end{tabular}
\label{fig:samples}
\caption{Sample underwater images displaying the diversity of distortion that can occur. \textbf{Maybe say something about how
some images lost all color, but some kept some color for close objects.}}
\end{figure}

Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision\starnote{Cite the
  canonical Deep Learning paper here please}. Often times, these networks require large amounts of data, either labeled or paired with
ground truth. For the problem of automatically colorizing grayscale images\starnote{CITE something on this?}, paired training data is
readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted by either
color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction. This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots\starnote{Summarize the approach here. Then talk about datasets as you have done already.} We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary domain $X$ to another arbitrary domain $Y$, as a way to generate a paired dataset. By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and $Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining ground truth.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
